Illustrating imputation of missing data using the Titanic dataset

### 2024-06-20 text/24/survival-lasso.Rmd
Update 2024 files

---
title: Illustrating the lasso model using the Worcester Heart Attack Study
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Survival analysis
- R programming
output: html_document
---

>>>>

---
title: Illustrating the lasso model using the Worcester Heart Attack Study
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Survival analysis
- R programming
output: html_document
page_update: complete
---

### 2024-06-20 text/24/titanic-imputation.Rmd
Update 2024 files

---
title: Illustrating imputation of missing data using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Missing data
- R programming
output: html_document
---

>>>>

---
title: Illustrating imputation of missing data using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Missing data
- R programming
output: html_document
page_update: complete
---
